---
title: "Coursera Machine Learning Project"
author: "Eli Miller"
date: "December 16, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Reading Data and variables
```{r, echo=FALSE, message=FALSE}
download.file('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv', 'pml-training.csv')
download.file('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv', 'pml-testing.csv')
training <- read.csv('pml-training.csv')
testing <- read.csv('pml-testing.csv')
library(caret)
```
After Data was read in, I subseted the `training` data to be every column except the ones with NA values, I also omitted the first seven, as they weren't movements by the user. This algorithm attempts to create 'connections' similar to those in the human brain.
```{r}
NAvalsTrn <- sapply(training, anyNA)
NAvalstst <- sapply(testing, anyNA)
NAvals <- (NAvalstst | NAvalsTrn)
noNATraining <- subset(training, select = !NAvals)
finalTrain <- subset(noNATraining, select = 8:60)
```
To speed up computations, I enabled parallel processing.
```{r}
library(parallel)
library(doParallel)
cluster <- makeCluster(detectCores() - 1)
registerDoParallel(cluster)
```
###Creating Model
Now I want to get ready to create the model. I made my `trainControl` object with bootstrapping with corrections. This should reduce over fitting somewhat.
```{r}
tc <- trainControl( allowParallel = TRUE, method = 'boot632')
```
I used a neural network to create the model. I choose this because I thought it would do the best job of modeling the complex behavior.
```{r cashe = TRUE, message=FALSE}
set.seed(123)
model <- train(classe~., data = finalTrain, method = 'nnet', trainControl = tc)
stopCluster(cluster)
registerDoSEQ()
```
###Prediction
With this model I can now predict on the testing set.
```{r}
model$finalModel
testing <- subset(testing, select = !NAvals)
preds <- predict(model,testing)
preds
```
The model did okay, but It seems the out-of-sample error was rather high. Principal 
Analysis could be a next step for this model to reduce this.
